Non-word repetition in Yélî Dnye

### 2020-06-09 manuscript.Rmd
added segment frequencies

- double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
- add frequency of sounds in stimuli in segments.xlsx from https://phoible.org/parameters
- then add that in stimuli to get minimum & average frequencies per stimulus
- then add analysis of NWR as a function of frequency
- draft discussion

@@

- look through for **mc**
- consent, "correct", "accuracy", "performance"
- help with table 1 (formatting)

>>>>

- double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
- finish integration in stimuli in wrangling.R to get minimum & average frequencies per stimulus
- then add analysis of NWR as a function of frequency
- draft discussion
- draft abstract

@@

- look through for **mc**
- double check my frequency entries in segments.xlsx using the search function in https://phoible.org/parameters; take a look at http://phoible.github.io/conventions/ in case you see something about double articulation (I didn't find tp or lBj)
- double check phonological implementation of stimuli in stimuli.xlsx, and if needed re-save as txt file to update the version read in this paper
- consent, "correct", "accuracy", "performance"
- help with table 1 (formatting & making it appear, because it's broken by the phonological representations)

### 2020-06-09 manuscript.tex
added segment frequencies

\begin{itemize}
\tightlist
\item
  double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
\item
  add frequency of sounds in stimuli in segments.xlsx from \url{https://phoible.org/parameters}
\item
  then add that in stimuli to get minimum \& average frequencies per stimulus
\item
  then add analysis of NWR as a function of frequency
\item
  draft discussion
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  look through for \textbf{mc}
\item
  consent, \enquote{correct}, \enquote{accuracy}, \enquote{performance}
\item
  help with table 1 (formatting)
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
\item
  finish integration in stimuli in wrangling.R to get minimum \& average frequencies per stimulus
\item
  then add analysis of NWR as a function of frequency
\item
  draft discussion
\item
  draft abstract
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  look through for \textbf{mc}
\item
  double check my frequency entries in segments.xlsx using the search function in \url{https://phoible.org/parameters}; take a look at \url{http://phoible.github.io/conventions/} in case you see something about double articulation (I didn't find tp or lBj)
\item
  double check phonological implementation of stimuli in stimuli.xlsx, and if needed re-save as txt file to update the version read in this paper
\item
  consent, \enquote{correct}, \enquote{accuracy}, \enquote{performance}
\item
  help with table 1 (formatting \& making it appear, because it's broken by the phonological representations)
\end{itemize}
